---
title: 'Alcohol-Related Crime Reduction Strategies for Restaurants and Nightlife in Arlington (ACPD)'
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    toc: yes
---

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# The Arlington Restaurants Initiative

  > The Police Department’s Arlington Restaurant Initiative was designed to address public safety issues, foster relationships and cooperation with businesses, and ultimately raise the best standards of restaurants that serve alcohol. The goal of the initiative is to develop strategies that will maintain Clarendon as a safe destination for nightlife and entertainment ([2017 Annual Report the Arlington County Police Department](https://arlingtonva.s3.amazonaws.com/wp-content/uploads/sites/11/2018/05/ACPD2017-Annual-Report.pdf)).

- In the news

  - [Best Bar None Goes USA](http://bbnuk.com/best-bar-none-goes-usa/)

  - [Sirens Wail in Clarendon as Targeted Police Efforts Focus on Bars and Restaurants](https://www.washingtoncitypaper.com/food/young-hungry/article/21001239/sirens-wail-in-clarendon-as-targeted-police-efforts-focus-on-bars-and-restaurants) (2018-04-18)

  - [Arlington County Police Department Trains TIPS to Reduce Alcohol-Related Harm](https://www.prnewswire.com/news-releases/arlington-county-police-department-trains-tips-to-reduce-alcohol-related-harm-300495817.html) (2017-07-28)

- ABC licensed 

# Housekeeping
<<<<<<< HEAD
```{r}
pacman::p_load(sdalr, DBI, httr, readr, stringr, dplyr, data.table, dtplyr)
=======
```{r housekeeping}
pacman::p_load(sdalr, DBI, httr, jsonlite, stringdist, sf, geosphere, tigris, lubridate, ggplot2, stringr, dplyr, data.table, dtplyr, purrr)
>>>>>>> 7ba5bb3494b51449452389d319399093ba770128
arlington_api_key = '140c712ce0aaf752160366975a7fa1cca8c81445'
```

# Helpers
```{r helpers}
geocode = function(address) {
  response = str_c('https://maps.googleapis.com/maps/api/geocode/json',
                    '?address=',
                   address,
                   '&key=',
                   google_api_key) %>%
    str_replace_all(pattern = '\\s',
                  replacement = '+') %>%
    GET()
  if (status_code(x = response) == 200L) {
    lon_lat = response %>%
      content(as = 'text',
              encoding = 'UTF-8') %>%
      fromJSON() %>%
      getElement(name = 'results')
    best_match = with(lon_lat,
                      which.min(x = stringdist(a = address,
                                               b = formatted_address)))
    lon_lat = lon_lat %>%
      getElement(name = 'geometry') %>%
      getElement(name = 'location') %>%
      filter(1:nrow(x = .) %in% best_match)
    output = data.table(address = address,
                        longitude = lon_lat$lng,
                        latitude = lon_lat$lat)
  } else {
    output = data.table(address = address,
                        longitude = NA,
                        latitude = NA)
  }
  return(value = output)
}
fixing_dates = function(dt) {
  m_d_y = str_split(string = dt,
                    pattern = '/') %>%
    unlist()
  output = str_c('20', m_d_y[3L], '-',
                 str_pad(string = m_d_y[1L],
                         width = 2L,
                         pad = '0',
                         side = 'left'),
                 '-',
                 str_pad(string = m_d_y[2L],
                         width = 2L,
                         pad = '0',
                         side = 'left'))
  return(value = output)
  }
```

# Alcohol Board Control (ABC) Virginia

- We identified all ABC-licensed restaurants in Arlington

```{r restaurants}
restaurants = function() {
  # Virginia Alcoholic Beverage Control Authority (VABC)
  # https://www.abc.virginia.gov/licenseesearch/retail_search_view.do
  # Select the data for all
  # - Establishment Type: Restaurant
  # - City/County: Arlington County
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  output = dbReadTable(con = conn,
                       name = 'vabc_arlington_restaurants')
  on.exit(expr = dbDisconnect(conn = conn))
  return(value = output)
}
restaurants = restaurants()
restaurants %>%
  select(trade_name, address) %>%
  unique() %>%
  head()
```

- Clarendon Metro Station as the centroid and a buffer of 0.25 miles.
```{r clarendon_metro}
clarendon_metro_station = c(-77.09499, 38.88718)
```

- We also identified the restaurants part of the ARI (sponsor-provided)
```{r air_restaurants}
ari_restaurants = c('Heavy Seas Alehouse',
                    'Irelands Four Courts',
                    'Samuel Becketts Irish Gastro Pub',
                    'Crystal City Sports Pub',
                    'Freddies',
                    'William Jeffreys Tavern',
                    'Whitlows On Wilson',
                    'Wilson Hardware',
                    'Bar Bao',
                    'Pamplona')
selected_restaurants = restaurants %>%
  select(trade_name, longitude, latitude) %>%
  filter(trade_name %in% ari_restaurants) %>%
  unique() %>%
  mutate(dist_from_clarendon = round(distm(x = select(.data = .,
                                                      longitude,
                                                      latitude),
                                           y = clarendon_metro_station) *
                                       6.21371e-4,
                                     digits = 2L) %>%
           as.numeric())
selected_restaurants %>%
  filter(dist_from_clarendon <= 2.5e-1) %>%
  pull(trade_name)
```

- How many restaurants are in the area of interest?
```{r clarendon_breakdown}
clarendon_restaurants = restaurants %>%
  select(trade_name, longitude, latitude) %>%
  unique()
clarendon_restaurants = clarendon_restaurants %>%
  mutate(dist_from_clarendon = round(distm(x = select(.data = clarendon_restaurants,
                                                      longitude,
                                                      latitude),
                                           y = clarendon_metro_station,
                                           fun = distVincentyEllipsoid) *
                                       6.21371e-4,
                                     digits = 2L) %>%
           as.numeric())
table(clarendon_restaurants$dist_from_clarendon <= 2.5e-1)
```

# Crime Incident Reports

- Source: [Police Incident Log](https://bit.ly/21nPzoE) "Arlington County Data API was used for this purpose, but it is not endorsed or certified by Arlington County."

- Temporal coverage: 2015-01-01 - Present (last updated 2018-06-14)

- Location: dbname = *acpd* / name = *crime*

```{r crime_incidence}
# crime_incidence = function(arlington_api_key) {
#   output = str_c('https://api.data.arlingtonva.us/api/v2/',
#                         'datastreams/POLIC-INCID-LOG-19589/data.csv/?auth_key=',
#                         arlington_api_key) %>%
#     GET() %>%
#     content(as = 'text', encoding = 'UTF-8') %>%
#     read_csv() %>%
#     mutate(firstReportDtm = as.POSIXct(x = firstReportDtm, tz = 'EDT'),
#            lastReportDtm = as.POSIXct(x = lastReportDtm, tz = 'EDT')) %>%
#     data.table() %>%
#     setnames(old = 'reportNbr', new = 'id') %>%
#     setnames(old = 'offenseDsc', new = 'description') %>%
#     setnames(old = 'locationName', new = 'location') %>%
#     setnames(old = 'latitudeCrd', new = 'latitude') %>%
#     setnames(old = 'longitudeCrd', new = 'longitude') %>%
#     setnames(old = 'firstReportDtm', new = 'start') %>%
#     setnames(old = 'lastReportDtm', new = 'end')
#   conn = con_db(dbname = 'acpd',
#                 pass = get_my_password())
#   dbWriteTable(con = conn,
#                name = 'crime',
#                value = output,
#                row.names = FALSE,
#                overwrite = TRUE)
#   on.exit(dbDisconnect(conn = conn))
#   }
# crime_incidence(arlington_api_key = arlington_api_key)
crime_incidence = function() {
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  output = dbReadTable(con = conn,
                       name = 'crime')
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
}
crime_incidence = crime_incidence()
head(x = crime_incidence)
```

- Alcohol-Related Crimes

```{r crime_types}
crime_type = c('DRUNK', 'DUI', 'ASSAULT', 'SEXUAL', 'DISORDERLY')
crime_regex = str_c('(', str_c(crime_type, collapse = '|'), ')')
print(crime_type)
```

```{r alcohol_crimes}
alcohol_crimes = crime_incidence %>%
  filter(str_detect(string = description,
                    pattern = crime_regex)) %>%
  mutate(id = 'Incident') %>%
  select(id, longitude, latitude) %>%
  mutate(dist_from_clarendon = round(distm(x = select(.data = .,
                                                      longitude,
                                                      latitude),
                                           y = clarendon_metro_station,
                                           fun = distVincentyEllipsoid) *
                                       6.21371e-4,
                                     digits = 2L) %>%
           as.numeric()) %>%
  filter(dist_from_clarendon <= 2.5e-1) %>%
  select(id, longitude, latitude)
```

```{r map}
data_map = clarendon_restaurants %>%
  filter(dist_from_clarendon <= 2.5e-1) %>%
  mutate(id = ifelse(test = trade_name %in% (selected_restaurants %>%
                                               filter(dist_from_clarendon <= 2.5e-1)
                                             %>%
                                               pull(trade_name)),
                     yes = 'ARI',
                     no = 'Restaurant')) %>%
  select(id, longitude, latitude) %>%
  rbind(alcohol_crimes)
va = county_subdivisions(state = 51L, # 'VA'
                         county = 013L, # 'Arlington County'
                         year = 2017L,
                         class = 'sf') %>%
  getElement(name = 'geometry')
upload_data_for_map = function() {
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  dbWriteTable(con = conn,
               name = 'for_map',
               value = data_map,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(dbDisconnect(conn = conn))
}
upload_data_for_map()
```

# ABC Violations

- Source: ABC Virginia [Hearing and Appeals: Final Decisions](https://www.abc.virginia.gov/enforcement/hearings-and-appeals/final-decisions/)

- [Glossary of Hearings and Appeals Terms](https://www.abc.virginia.gov/enforcement/hearings-and-appeals/key-terms/)

- Manually updated

- Temporal coverage (2014-07-01 - 2017-06-31)

- Location: dbname = *acpd* / name = *abc*

```{r abc}
abc = function() {
<<<<<<< HEAD
  conn = con_db(dbname = 'oss',
=======
  conn = con_db(dbname = 'acpd',
>>>>>>> 7ba5bb3494b51449452389d319399093ba770128
                pass = get_my_password())
  output = dbReadTable(con = conn,
                       name = 'geocoded') %>%
    data.table()
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
}
abc = abc()
head(x = abc)
```
<<<<<<< HEAD
=======

Participating restaurants

```{r cleaning_abc}
# arlington_address_geocoded = map_df(.x = abc %>%
#                                       filter(city %in% 'ARLINGTON') %>%
#                                       pull(address) %>%
#                                       unique() %>%
#                                       str_c(' Arlington, VA'),
#                                     .f = geocode)
upload_geocoded = function() {
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  dbWriteTable(con = conn,
               name = 'geocoded',
               value = arlington_address_geocoded,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(dbDisconnect(conn = conn))
  }
# upload_geocoded()
read_geocoded = function() {
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  output = dbReadTable(con = conn,
                       name = 'geocoded') %>%
    data.table()
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
}
arlington_address_geocoded = read_geocoded()
upload_abc_clean = function() {
  output = merge(x = abc %>%
                   filter(city %in% 'ARLINGTON'),
                 y = arlington_address_geocoded %>%
                   mutate(address = str_extract(string = address,
                                                pattern = '.*(?= Arlington, VA)'))) %>%
    mutate(date_available_to_ha = map_chr(.x = date_available_to_ha,
                                          .f = fixing_dates) %>%
             as.Date(),
           date_violation = map_chr(.x = date_violation,
                                    .f = fixing_dates) %>%
             as.Date(),
           date_heard = map_chr(.x = date_heard,
                                .f = fixing_dates) %>%
             as.Date(),
           date_decision =  map_chr(.x = date_decision,
                                    .f = fixing_dates) %>%
             as.Date(),
           date_disposition = map_chr(.x = date_disposition,
                                      .f = fixing_dates) %>%
             as.Date(),
           civil_penalty_in_usd = civil_penalty_in_usd %>%
             str_remove_all(pattern = '(\\$|,)') %>%
             as.numeric(),
           civil_penalty_in_usd = 
             ifelse(test = is.na(x = civil_penalty_in_usd),
                    yes = 0,
                    no = civil_penalty_in_usd))
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  dbWriteTable(con = conn,
               name = 'abc_cleaned',
               value = output,
               row.names = FALSE,
               overwrite = TRUE)
  on.exit(dbDisconnect(conn = conn))
  }
upload_abc_clean()
read_abc_clean = function() {
  conn = con_db(dbname = 'acpd',
                pass = get_my_password())
  output = dbReadTable(con = conn,
                       name = 'abc_cleaned')
  on.exit(dbDisconnect(conn = conn))
  return(value = output)
}
abc_clean = read_abc_clean()
head(x = abc_clean)
```
>>>>>>> 7ba5bb3494b51449452389d319399093ba770128
